% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper, 11pt]{article}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.54}
%\usepackage{libertine}
\usepackage{enumitem}

\usepackage[utf8]{inputenc}
\usepackage{eurosym}
\exhyphenpenalty=10000
\hyphenpenalty=10000
\widowpenalty=10000
\clubpenalty=10000


% Set your name here
\def\name{Tiago Ventura}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://danilofreire.com/DaniloFreireCV.pdf}

% The following metadata will show up in the PDF properties

\hypersetup{
	colorlinks = true,
	urlcolor = darkblue,
	pdfauthor = {\name},
	pdfkeywords = {social media, computational methods, comparative politics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in, 8.5in},
	left=1.0in,
	top=2.5cm,
	bottom=2.5cm
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewcommand{\labelitemi}{}


% change enum

\renewcommand{\labelenumi}{[\arabic{enumi}]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}[leftmargin=2em]
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
	
	% Place name at left
	{\huge \name}
	
	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}
	
	\vspace{0.25in}
	
	\begin{minipage}{0.45\linewidth}
		McCourt School of Public Policy\\
		Georgetown University,  \\
		Washington DC 
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\begin{tabular}{ll}
			Email:          & \href{mailto:tv186@georgetown.edu}{tv186@georgetown.edu}          \\
			Homepage:       & \href{http://venturatiago.com/}{http://venturatiago.com}             \\
			GitHub:         & \href{https://github.com/TiagoVentura}{https://github.com/TiagoVentura}
		\end{tabular}
	\end{minipage}


\section*{Academic Positions and Affiliations}

{\textbf{Georgetown University}}

Assistant Professor, McCourt School of Public Policy (2023 - ).
\vspace{.3cm}

{\textbf{Center for Social Media and Politics (CSMaP), New York University}}

Postdoctoral Associate (2022-2023).

\vspace{.3cm}

\textbf{Twitter, Experience Research Team}

Researcher on Civic Integrity and Misinformation (2021-2022)
			
\section*{Education}
	
\textit{\textbf{University of Maryland, College Park.}}

Ph.D., Political Science, 2022.

M.A.,  Political Science, 2020
     
\vspace{.3cm}

\textit{\textbf{State University of Rio de Janeiro, Brazil}}

Ph.D. and M.A. Political Science, 2019

\vspace{.3cm}

\textit{\textbf{Federal University of Para, Brazil}}

B.A.,  Law.
		
\section*{Peer-Reviewed Publications}
	
     \begin{benumerate}{20}

        \item Steven Rathje*, Nejla Asimovic*, \textbf{Tiago Ventura}*,  Sarah Mughal, Claire E. Robertson, Christopher Barrie, Joshua Tucker, and Jay J. Van Bavel. \href{https://osf.io/preprints/psyarxiv/ujtxa_v1}{Testing the Causal Impact of Social Media Reduction Around the Globe} \textit{Stage 1 Registered Report Accepted in Principle at Nature} *[equal co-first author]

      \item Toney-Wails, Autumn, Bode, Leticia, \textbf{Ventura, Tiago}, Wilcox, Ethan, and Singh, Lisa. Comparing the Humanness of Machine-Generated and Human-Authored Text. \textit{Forthcoming at ACM Computing Surveys}

      \item  Clemm von Hohenberg, Bernhard; \textbf{Ventura, Tiago}, Nagler, Jonathan; Menchen-Trevino, Ericka; Magdalena, Wojcieszak, 2025 \href{https://www.cambridge.org/core/journals/political-analysis/article/survey-professionalism-new-evidence-from-web-browsing-data/552625B9C6C5F32BA1DD69435043C184}{Survey Professionalism: New Evidence from Browsing Data} \textbf{Political Analysis} 

        \item \textbf{Ventura, Tiago}*; Majumdar, Rajeshwari; Nagler, Jonathan; Tucker, Joshua A., 2025 \href{https://www.journals.uchicago.edu/doi/epdf/10.1086/737172}{Misinformation Beyond Traditional Feeds: Evidence from a WhatsApp Deactivation Experiment in Brazil} Forthcoming at  \textbf{The Journal of Politics} *[first author]   

        \subitem \textit{Winner of the 2024 Paul Lazarsfeld Best Paper Award, recognizing the best overall paper presented on the topic of Political Communication at the 2023 APSA meeting}
        \subitem  \textit{Winner of the 2024 Information Technology and Politics Award recognizing the best overall paper presented on the topic at the 2023 APSA meeting}
       \subitem \textit{Winner of the 2024 Best Paper in Political Behavior presented at the Brazilian Political Science Association Meeting}
       \subitem \textit{Winner of the 2024 Best Overall Paper presented at the Brazilian Political Science Association Meeting}

       \item  Aruguete, Natalia; Calvo, Ernesto; Scarstacini, Carlos; \textbf{Ventura, Tiago}, 2025 \href{https://www.tandfonline.com/doi/full/10.1080/19331681.2025.2502503}{Keep your promises, even when your peers do not: A Survey Experiment on the Influence of Social Media on Trust} 
       Journal of Information, Technology and Politics 1–18. *[equal authorship]


        \item Aruguete, Natalia, Calvo, Ernesto, \& \textbf{Ventura, Tiago}, 2025 \href{https://journals.sagepub.com/doi/10.1177/20531680251323120}{The Fact-Checking Dilemma: Fact-Checking increases the reputation of the fact-checker but creates perceptions of ideological bias}.  Research and Politics *[equal authorship]

       \item Aruguete, Natalia; Batista, Flavia, Calvo; Ernesto, Guizzo-Altube, Mateo; Scartascini, Carlos, \& \textbf{Ventura, Tiago}, 2024. \href{https://www.nature.com/articles/s41598-024-53337-0}{Framing fact-checks as a “confirmation” increases engagement with corrections of misinformation: a four-country study}. Nature: Scientific Reports, 14(1), 3201. *[equal authorship]

       \item \textbf{Ventura, Tiago}*; Ley, Sandra; Cantu, Francisco, 2024. \href{https://journals.sagepub.com/doi/10.1177/00104140231169035}{Voting for Law and Order: Evidence from a Survey Experiment in Mexico}, \textit{Comparative Political Studies} 57(4), pp.551-583. *[first-author]	

        \item Aruguete, Natalia; Bachman, Ingrid; Calvo, Ernesto; Valenzuela, Sebastian \textbf{Ventura, Tiago*}, 2023. \href{https://journals.sagepub.com/doi/abs/10.1177/14614448231193709}{Truth be told: Cognitive moderators of selective sharing of fact-checks on social media} \textit{New Media \& Society}, 0(0)  *[equal authorship]	
	

        \item Kesari, Aniket; Kim, Jae Yeon;  Shah, Sono ; Brown, Taylor Law, Tina; \textbf{Ventura, Tiago}, 2023. \href{https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/training-computational-social-science-phd-students-for-academic-and-nonacademic-careers/1455690939833B9FFCAC664D4E412057}{Training Computational Social Science Ph.D. Students for Academic and Non-Academic Careers}  \textit{(PS: Political Science \& Politics), , 1-6.} 

        \item Calvo, Ernesto; \textbf{Ventura, Tiago}; Aruguete, Natalia; Waisboard, Silvio, 2023. \href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0281475}{Winning! Election returns and engagement in social media}, \textit{PLOS ONE 18(3): e0281475}
		
        \item Aruguete, Natalia; Calvo, Ernesto; \textbf{Ventura, Tiago}*, 2022. \href{https://academic.oup.com/joc/advance-article/doi/10.1093/joc/jqac035/6767335?searchresult=1}{Network activated frames: content sharing and perceived polarization in social media}, \textit{Journal of Communication}, Volume 73, Issue 1, February 2023, Pages 14–24.	*[equal authorship]	
        
        \item Aruguete, Natalia; Calvo, Ernesto; \textbf{Ventura, Tiago}*, 2022. \href{https://journals.sagepub.com/doi/abs/10.1177/19401612211057068}{News by Popular Demand: Ideology, Reputation, and Issue Attention in Social Media News Sharing}, \textit{The International Journal of Press/Politics.}, 0(0). *[equal authorship]	
        
		
        \item  Asbury, Victoria; Keng-Chi, Keng; McCabe, Katherine; Munger, Kevin; \textbf{Ventura, Tiago}*, 2021. \href{https://academic.oup.com/joc/article-abstract/71/6/947/6415947}{The Effect of Streaming Chat on Perceptions of Debates},  \textit{Journal of Communication, Volume 71, Issue 6}. *[equal authorship]	
        
        \item Aruguete, Natalia; Calvo, Ernesto; Cantu, Francisco; Ley, Sandra; \textbf{Ventura, Tiago}*; Scartascini, Carlos, 2021. \href{https://www.tandfonline.com/doi/abs/10.1080/17457289.2021.1924740}{Partisan Cues and Perceived Risks: The effect of partisan social media frames during the Covid-19 crisis in Mexico},  \textit{Journal of Elections, Public Opinion and Parties} 31(sup1), pp.82-95. *[equal authorship]	
        
        \item \textbf{Ventura, Tiago}*;  Munger, Kevin; Keng-Chi, Keng; McCabe, Katherine, 2021. \href{https://journalqd.org/article/view/2573}{Connective Effervescence and Streaming Chat
        During Political Debates}, \textit{Journal of Quantitative Description, Digital Midia} 1. *[equal authorship]	
        
        \item  Calvo, Ernesto; \textbf{Ventura, Tiago}*, 2021. \href{http://venturatiago.com/files/Calvo_Ventura_Covid_Social_Media.pdf}{Will I get COVID-19? Partisanship, Social Media Frames, and Perceptions of Health Risk in Brazil}, \textit{Latin American Politics and Society, 1-26}.*[equal authorship]	
        
        \item  Aruguete, Natalia; Calvo, Ernesto; \textbf{Ventura, Tiago}*, 2021. \href{https://www.tandfonline.com/doi/abs/10.1080/21670811.2020.1852094}{Polarization, News Sharing, and Gatekeeping: A study of the Bolsonaro Election}, \textit{Digital Journalism, 9:1, 1-23}. *[equal authorship]	
        	
        \item \textbf{Ventura, Tiago}, 2021. \href{https://www.sciencedirect.com/science/article/pii/S0261379420301219?dgcid=author}{Do Mayors Matter? Reverse Coattails on Congressional Elections in Brazil}, Electoral Studies, 69:102242.
            \begin{itemize}[leftmargin=*]
            \item \textit{Winner of the Donald C. Piper Award, Best Graduate Student Research Paper, GVPT, UMD}
            \end{itemize}
	
 	
    \end{benumerate}


\section*{Working Papers}

\subsection*{Under Review}
    \begin{benumerate}{4}

       \item Majumdar, Rajeshwari*; Ventura, Tiago*; Liu, Shelley; Torreblanca, Carolina; Tucker, Joshua. \textbf{Reducing WhatsApp Usage to Mitigate Misinformation Exposure During Elections: Evidence from a Multi-Country Experiment} \textit{Under Review} *[equal co-first author]

       \subitem \textit{Winner of the 2025 MPSA Best Paper Award in Political Behavior}
         
        \item  Megan Brown, Tiago Ventura, Joshua A. Tucker, Jonathan Nagler. \textbf{The relationship between offline partisan geographical segregation and online partisan segregation}  \textit{Under Review} 
      	
        \item Ventura, Tiago*; Bisbee, Jim; Graham, Sarah; Tucker, Joshua \textbf{Understanding Beliefs in Misinformation: Repetition, Partisan Signals and Bayesian Processing} \textit{Under Review} *[first author] 

        \item Paik, Sejin; Ventura, Tiago; Ansell, Rebecca; Toney-Wails, Autumn; Bode, Leticia;  Singh, Lisa \textbf{Human-authored or AI-generated? Humans can usually tell the difference for political content on social media platforms} \textit{Under Review}
   
        %\item\href{https://venturatiago.com/files/ventura_voting_for_violence_jmp.pdf}{Voting for Violence: Criminal Violence and the Election of Law and Order Politicians in Brazil} \textbf{R\&R at Comparative Politics} 
        
        %\subitem \textit{Winner of the Mario Fuks Awards - Best Paper in the Political Behavior Section of  the Brazilian Political Science Political Behavior.}
      		
        \end{benumerate}

\subsection*{In Preparation}

    \begin{benumerate}{3}

         \item Vallejo, Sebastian; Ventura, Tiago; Wu, Patrick*. \textbf{Using Large Language Models and Text-Completion to Augment Web-Browsing Data} \textit{Presented at APSA 2025}*[equal contribution]

        \item Ventura, Tiago*; Barrie, Christopher; Roberts, Margaret E.; Schwarz, Christopher; Tucker, Joshua A. \textbf{Echo Chambers After the Ban: Political Information on X in Brazil} \textit{Presented at APSA 2025}*[First author]
      					
         \item Lucia Tiscornia, Sandra Ley, and Tiago Ventura. \textbf{Criminal governance amid the COVID-19 pandemic in Mexico}. \textit{Writing}

       
    
     \end{benumerate}


    \section*{Peer-Reviewed in Portuguese}    		
		
    \begin{benumerate}{4}
	
    \item  Santos, Fabiano; Tanscheit, Talita; \textbf{Ventura, Tiago}*, 2020. \href{https://www.scielo.br/pdf/dados/v63n3/0011-5258-dados-63-3-e20180152.pdf}{ O Partido dos trabalhadores e as instituições Participativas: a influência da dinâmica intrapartidária na adoção do Orçamento Participativo}, \textit{DADOS, Rio de Janeiro, vol.63(3)}. *[equal authorship]
	
	     
	\item  Pogrebinschi, Thamy,  \textbf{Ventura, Tiago}*, 2017. \href{http://www.scielo.br/scielo.php?pid=S0011-52582017000100007&script=sci_abstract}{ Mais Particip\c{c}\~ao, Maior Responsividade? As Confer\^encias Nacionais de Pol\'iticas P\'ublicas e a Qualidade da Democracia no Brasil}, Revista Dados, Rio de Janeiro. *[equal authorship]
		
	
        \item Maciel, Natalia,  \textbf{Ventura, Tiago}*, 2017. \href{http://www.scielo.br/pdf/op/v23n1/1807-0191-op-23-1-0096.pdf}{O Partido dos Trabalhadores na C\^amara dos Deputados: a evolu\c{c}\~{a}o das bases socioecon\'omicas e territoriais (1994-2014)}, Revista Opini\~ao P\'ublica, Campinas. *[equal authorship]
		
	
        \item \textbf{Ventura, Tiago}, 2016. \href{http://www.scielo.br/pdf/cebape/v14n3/1679-3951-cebape-14-03-00705.pdf}{``Democracia e participa\c{c}\~ao. Inova\c{c}\~oes democr\'aticas e trajet\'oria participativa no Brasil''},  Cadernos Ebape, FGV, Rio de Janeiro.
	
    \end{benumerate}
		


\section*{Non Peer-Reviewed Articles \& Book Chapters}
		
    \begin{benumerate}{3}

    \item \textbf{Ventura, Tiago}*, Ansell, Rebecca; Paik, Sejin; Toney, Autumn; Bode, Leticia; Singh, Lisa, 2024. Analyzing the perceived humanness of AI-generated social media content around the presidential debate, US Election Analysis 2016: Media, Voters and the Campaign, edited volume. *[first author]

    % need to ad robert book chapter
            
    \item   Calvo, Ernesto and \textbf{Ventura, Tiago}*, 2022. Percepcion subjetiva de riesgo e identidades politicas en Brasil, \textit{Voces del Fenix, 86: pg. 85. Buenos Aires: Argentina}.*[equal authorship]
	
    \item  Calvo, Ernesto; Timoneda, Joan; \textbf{Ventura, Tiago}*, 2020. Big Relational Data: Network-Analytic Measurement, \textit{The SAGE Handbook of Research Methods in Political Science and International Relations}. *[equal authorship]
	
    \end{benumerate}
	
	
% \subsection*{In Preparation (Drafts Available Upon Request)}

% \begin{itemize}
% 		\item Voting for Violence: Criminal Violence and the Election of Law and Order Politicians in Brazil \textit{(Dissertation Chapter)}
		
% 		\item Legislating for Violence: Issue Ownership and Occupational Heuristics in the Brazilian Congress \textit{(Dissertation Chapter)}

% 		\item Voting for Law and Order and Criminal Violence in Mexico: A Network Approach. (With Francisco Cantu and Sandra Ley) \textit{Dissertation Chapter}

% 		\item The Electoral Cycle of Killing (With Mariana Carvalho) 
		


\section*{Grants, Fellowships and Awards}
	\begin{itemize}[leftmargin=.45cm]
        \item \textbf{2025} - Winner of the 2025 MPSA Best Paper in Political Behavior Award
        \item \textbf{2024} - Winner of the 2024 Paul Lazarsfeld Best Paper Award, recognizing the best overall paper presented on the topic of Political Communication at the 2023 APSA meeting.
        \item \textbf{2024} - Tech \& Public Policy Grant, McCourt School of Public Policy \& Project Liberty. Generative AI, Humanness, and Misinformation in the 2024 US Presidential Election, Co-PI with Lisa Singh and Leticia Bode (\$ 440,000) 
        \item \textbf{2023} - Tech \& Public Policy Grant, McCourt School of Public Policy \& Project Liberty. The Effects of WhatsApp on Politics: A Multi-Country Deactivation Experiment, Co-PI with Joshua Tucker (\$294,494) 
 		\item \textbf{2022} - \href{https://www.siegelendowment.org/}{Siegel Family Endowment}, Research Fellow, Cohort 2022 - 2023	
	    \item \textbf{2021} - EGAP Small Grant: Issues of governance relating to the COVID-19 pandemic (\$10,000) with Sandra Ley and Lucia Tiscornia.
           \item \textbf{2021} - Mario Fuks Awards - Best Paper in the Political Behavior in the Brazilian Political Science Political Behavior Meeting
	    \item \textbf{2021} - Donald C. Piper Award for Best Graduate Student Research Paper, Government and Politics, UMD.
	    \item \textbf{2021} - Young Talent in Computational Social Science Fellowship - Getulio Vargas Foundation, Rio de Janeiro (\$15,000). 
		\item \textbf{2020} - College of Behavioral Social Science, University of Maryland. Dean's Research Initiative (DRI), Doctoral Dissertation Research 2020 (\$2.500)
		\item \textbf{2019} - The Effect of Streaming Chat on Perceptions of Debates, Russel Sage Foundation (\$6.000) (With Victory Asbury, Keng-Chi Chang, Katherine McCabe, and Kevin Munger)
		\item \textbf{2019} - Graduate School University of Maryland, Summer Fellowship(\$5.000)
		%\item APSA Travel Conference Scholarship, 2018.
		%\item Government and Politics Political Theory and Methodology Training Award, 2018 (\$1.000)
		\item \textbf{2017} - University of Maryland, Dean's Summer Fellowship (\$5.000) 
		\item \textbf{2015} - DAAD (German Academic Exchange Service) Fellowship,  Short-time research in Germany (\euro{} 4.000)
		\item \textbf{2013} - State of Rio de Janeiro, The best GPA for Graduate Students in the State of Rio de Janeiro (R\$ 24.000)
	\end{itemize}

 \section*{Invited Talks \& Conferences}
    \begin{itemize}[leftmargin=0cm, noitemsep]
    % 2025
     \item \textbf{2025:} \hspace{.02cm} George Washington University - CP Workshop
    \item \hspace{1.25cm} Columbia University - Media Effects Workshop
    \item \hspace{1.25cm} Annual Conference Center for Social Media and Politics - New York University 
    \item \hspace{1.25cm} COMPPIT - Law School Getulio Vargas Foundation
    \item \hspace{1.25cm} Georgetown University - Mortara Center Research Seminar
    %2024
    \item \textbf{2024:} \hspace{.02cm} InterAmerican Bank of Development - Development Workshop.
    \item \hspace{1.25cm} University of Mancherster, Social Media, Misinformation, War Workshop. 
    \item \hspace{1.25cm} CIVICA Social Data Science series - European University Institute
     \item \hspace{1.25cm} Annual Conference Center for Social Media and Politics - New York University 
      \item \hspace{1.25cm} Invited Speaker Interdisciplinary Lab in CSS - University of Maryland 
    \item \textbf{2023:} \hspace{.02cm} Conference on Digital Experimentation @ MIT - CODE@MIT 
    \item \hspace{1.25cm} The Post-API Conference, University of Pennsylvania.
    \item \hspace{1.25cm} Politics and Computational Social Science (PaCSS):
    \item \hspace{1.25cm} American Political Science Association, Los Angeles
    \item \hspace{1.25cm} Annual Meeting of the Society for Political Methodology
    \item \hspace{1.25cm} Midwest Political Science Association, Chicago
    \item \hspace{1.25cm} Computational and Experimental Lab in Political Science, Federal University of Pernambuco.
    \item \hspace{1.25cm} Comparative Politics Workshop, University of Washington, Seattle.
    \item \hspace{1.25cm}  Siegel Foundation Conference, New York City.
    \item \hspace{1.25cm}  Conference Social Media and Democracy, Sciences Po, Paris.
    
    \vspace{.2cm}
    
    \item \textbf{2022:} \hspace{.02cm} Big Data and Governance Conference, University of Pennsylvania.
    \item \hspace{1.25cm} American Political Science Association, Canada
    \item \hspace{1.25cm}  External Speaker Series - State University of Rio de Janeiro.
    \item \hspace{1.25cm}  Digital Misinformation in the Global South (DIMIS).
    
    \vspace{.2cm}
    
    \item \textbf{2021:} \hspace{.02cm} Social Data Science Center, University of Maryland.
    \item \hspace{1.25cm}  Data-Science Workshop, Georgetown McCourt School.
    \item \hspace{1.25cm}  World Association for Public Opinion Research (WAPOR) Latin America 
    \item \hspace{1.25cm} Political Networks Conference (POLNET)
    \item \hspace{1.25cm} Midwest Workshop in Empirical Political Science, 2021, Purdue.
   \item \hspace{1.25cm} Brazilian Political Science Meeting, Political Behavior Section
\end{itemize}

%\section*{Conferences}}
     
 %   \begin{itemize}[leftmargin=.45cm}
  %  \item American Political Science Association: 2023, 2022, 2019, 2018.
   % \item Midwest Political Science Association: 2023, 2019, 2018, 2017.
    %\item Annual Meeting of the Society for Political Methodology: 2023
    %\%item Political Networks Conference (POLNET): 2021
   % \item Brazilian Political Science Meeting, Political Behavior Section, 2021. 
    %\item Politics and Computational Social Science (PaCSS): 2023, 2020, 2019.
    %\item Empirical Implications of Theoretical Models: 2019.


\section*{Teaching}
	
	\begin{itemize}[leftmargin=.45cm]
		\item \textbf{At Georgetown University}
             \subitem \href{https://tiagoventura.github.io/ppol5203/}{PPOL 5203: Data Science I - Foundations}, Master in Data Science \& Public Policy
             \subitem \href{https://tiagoventura.github.io/PPOL_6801/}{PPOL 6801: Text as Data - Computational Linguistics}, Master in Data Science \& Public Policy
    
   %\href{https://github.com/TiagoVentura/workshop_big_data_conference}{Collecting and Analyzing Social Media Data} UPenn, 2022
	
 
         \item \textbf{At Getulio Vargas Foundation }
         \subitem \href{https://fgvintrocss.netlify.app/}{Introduction to Computational Social Science} Undergraduate Course, FGV-RJ, Brazil, 2021
		%\item \href{http://datavizgvpt.tiagoventura.rbind.io/}{Data Visualization (Tidying your model into a nice plot)}, GVPT, UMD, 2020.
		%\item \href{https://tiagoventura.github.io/workshop_ufpa/}{Collecting online data in R}, Federal University of Para, 2019.
		%\item \href{http://venturatiago.com/files/gsa_tidyverse_workshop/}{Introduction to Tidyverse}, University of Maryland, 2019.
		%\item \href{https://github.com/TiagoVentura/UMD_workshop_Rpackages}{How to build an R Package}, University of Maryland, 2018.
	\end{itemize}

	

	
% \section*{Skills}
	
%     \subsection*{Software}
	
% 	\begin{itemize}[leftmargin=.45cm]
% 		\item Python, R,  git, SQL, \LaTeX{}, Markdown, HTML, CSS.
% 	\end{itemize}
	
%     \subsection*{Languages}
	
% 	\begin{itemize}[leftmargin=.45cm]
% 		\item Portuguese (native), English (fluent), Spanish (intermediate)
% 	\end{itemize}
	
		

% 	\section*{Software}
	
% 	\begin{itemize}
% 		\item \href{https://github.com/TiagoVentura/GetIRdata}{GetIRdata}. R package to download and merge data commonly used in International Relations.
% 		\item \href{https://github.com/TiagoVentura/pwr}{PWR}. R package to implement our Path Weighted Regression for Big Network Models. 
% 	\end{itemize}
	
	
\section*{Service}
	
    \begin{itemize}[leftmargin=.45cm]
	\item \textbf{Reviewer:} \textit{Nature Human Behavior; Nature Communications; American Political Science Review; American Journal of Political Science; Political Analysis; PLOS One; Social Media + Society; International Journal of Press/Politics; Journal of Politics; Political Geography; Electoral Studies; Journalism and Mass Communication Quarterly; Legislative Studies Quarterly; The Communication Review, Information,Communication \& Society; Digital Journalism; Perspective on Politics; Latin Amerinca Politics and Society; Dados; Opiniao Publica} 
	\end{itemize}
	
	
    \begin{itemize}[leftmargin=.45cm]
		
            \item Search Committee - Assistant Professor in Computational Social Sciences, Georgetown`s McCourt School of  Public Policy
            \item Search Committee for the Chair of the Government and Politics Department, University of Maryland, College Park.
		\item Graduate Student Methods Representative 2018-2019, GVPT, UMD. 
		\item Dean's Graduate Student Advisory Committee - GVPT Representative 2018-2019.
    \end{itemize}
	
% 	\section*{References}
	
% 	\begin{itemize}
% 		\item Ernesto Calvo. Professor,University of Maryland, College Park. Email: \href{mailto:ecalvo@umd.edu }{ecalvo@umd.edu }
% 		\item William Reed, Professor, University of Maryland, College Park. Email: \href{mailto:wlr@umd.edu }{wlr@umd.edu}
% 		\item Isabella Alca\~niz. Professor, University of Maryland, College Park. Email: \href{mailto:ialcaniz@umd.edu }{ialcaniz@umd.edu}
% 		\item Ariel White. Assistant Professor, MIT, . Email: \href{mailto:arwhi@mit.edu}{arwhi@mit.edu}
% 		\item Kevin Munger. Assistant Professor, Penn State, . Email: \href{mailto:kmm7999@psu.edu}{kmm7999@psu.edu}
		
% 		% \item Sandra Ley. Assistant Professor, CIDE-Mexico, . Email: \href{mailto:sandra.ley@cide.edu}{sandra.ley@cide.edu}
		
% 	\end{itemize}
	
	\bigskip
	
	% Footer
	\begin{center}
		\begin{footnotesize}
			Last updated: \today
		\end{footnotesize}
	\end{center}
	
\end{document}